Waiting time analysis

### 2025-06-21 notebooks/21_model.qmd
fig: mva and cross comparison

```{julia}
using Discontinuity
using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta, filter_low_mva_quality!
using Juno: produce_or_load_juno
using Juno.Data: get_mag_data, get_state_data, read_sw_params_csv
using CairoMakie
using AlgebraOfGraphics
import SPEDAS
set_aog_theme!()
theme = Theme(; figure_padding=(0, 6, 0, 0),
    Legend=(padding=(0, 0, 0, 0), margin=(0, 0, 0, 0),)
)
update_theme!(theme)
```

@@

let df = filter_low_mva_quality!(jno_df_with_params), xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
    f = Figure(;)
    wh = (width=120, height=110)
    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel, wh...)
    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), wh..., axis...)

@@

@@

    lines!(ax2, exp10.([-1.5, 0]), exp10.([-1.5, 0]); color, linestyle)
    lines!(ax_L, exp10.([2, 5]), exp10.([2, 5]); color, linestyle)
    lines!(ax_J, exp10.(-2:1), exp10.(-2:1); color, linestyle)
    lines!(ax_Ln, exp10.([-1, 3]), exp10.([-1, 3]); color, linestyle)
    lines!(ax_Jn, exp10.([-2, 2]), exp10.([-2, 2]); color, linestyle)
    lines!(ax_T, exp10.([0.2, 1.5]), exp10.([0.2, 1.5]); color, linestyle)
    lines!(ax_β, exp10.(-2:2), exp10.(-2:2); color, linestyle)

@@

>>>>

```{julia}
using Discontinuity
using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta, filter_low_mva_quality
using Juno: produce_or_load_juno
using Juno.Data: get_mag_data, get_state_data, read_sw_params_csv
using CairoMakie
using AlgebraOfGraphics
import SPEDAS
set_aog_theme!()
theme = Theme(; figure_padding=(0, 6, 0, 0),
    Legend=(padding=(0, 0, 0, 0), margin=(0, 0, 0, 0),)
)
update_theme!(theme)
```

@@

let df = filter_low_mva_quality(jno_df_with_params), xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
    f = Figure(;)
    wh = (width=120, height=110)
    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel, wh...)
    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), wh..., axis...)

@@

    # Compare L and J from MVA and cross methods
    ax_L_comp = Axis(f[3, 2]; title=lru("L", u"km"), xlabel="MVA", ylabel="Cross", wh..., axis...)
    ax_J_comp = Axis(f[3, 3]; title=lru("J", u"nA/m^2"), xlabel="MVA", wh..., axis...)

    @with df begin
        uless_plot!(ax_L_comp, :L_n_mva_sw, :L_n_cross_sw; plot...)
        uless_plot!(ax_J_comp, :J_m_max_mva_sw, :J_m_max_cross_sw; plot...)
    end

@@

    lines!(ax2, exp10.([-1.5, 0]), exp10.([-1.5, 0]); color, linestyle)
    lines!(ax_L, exp10.([2, 5]), exp10.([2, 5]); color, linestyle)
    lines!(ax_J, exp10.(-2:1), exp10.(-2:1); color, linestyle)
    lines!(ax_Ln, exp10.([-1, 3]), exp10.([-1, 3]); color, linestyle)
    lines!(ax_Jn, exp10.([-2, 2]), exp10.([-2, 2]); color, linestyle)
    lines!(ax_T, exp10.([0.2, 1.5]), exp10.([0.2, 1.5]); color, linestyle)
    lines!(ax_β, exp10.(-2:2), exp10.(-2:2); color, linestyle)
    lines!(ax_L_comp, exp10.([2, 5]), exp10.([2, 5]); color, linestyle)
    lines!(ax_J_comp, exp10.([-2, 1]), exp10.([-2, 1]); color, linestyle)

@@

    limits!(ax_L_comp, 10^2.5, 10^5.1, 10^2.5, 10^5.1)
    limits!(ax_J_comp, 10^-2.1, 10^1.1, 10^-2.1, 10^1.1)
